% ==========================================================================
% My (LaTeX) resume
% ==========================================================================
%
% Original author: Sourabh Bajaj (https://github.com/sb2nov/resume)
% License: MIT
%
% ==========================================================================

\documentclass[11pt, a4paper]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{tikz}
\usepackage[sfdefault,light]{FiraSans} % https://tug.org/FontCatalogue/ %
\usepackage[T1]{fontenc}

\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand*\oldstylenums[1]{{\firaoldstyle #1}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% ==========================================================================
% Custom commands
% ==========================================================================

\newcommand{\resumeItem}[1]{
  \item\small{
    #1
  }
}

% \newcommand{\resumeSubheading}[4]{
%   \item
%     \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
%       \textbf{#1} & \small{#2}\vspace{2pt}\\
%       \small{#3} & \small{#4}\\
%     \end{tabular*}
% }

\newcommand{\resumeSubheading}[3]{
  \item
    \begin{tabularx}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}c@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{#2} & \textbf{#3}
    \end{tabularx}
}

\newcommand{\resumeSubSubheading}[2]{
  \begin{tabularx}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \vspace{10pt}\textbf{#1} & \textbf{#2}
  \end{tabularx}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}}

\newcommand{\externalLink}{%
  \tikz[x=1.2ex, y=1.2ex, baseline=-0.05ex]{%
    \begin{scope}[x=1ex, y=1ex]
      \clip (-0.1,-0.1)
        --++ (-0, 1.2)
        --++ (0.6, 0)
        --++ (0, -0.6)
        --++ (0.6, 0)
        --++ (0, -1);
      \path[draw,
        line width = 0.5,
        rounded corners=0.5]
        (0,0) rectangle (1,1);
    \end{scope}
    \path[draw, line width = 0.5] (0.5, 0.5)
      -- (1, 1);
    \path[draw, line width = 0.5] (0.6, 1)
      -- (1, 1) -- (1, 0.6);
    }
  }

% ==========================================================================


% ==========================================================================
% Resume starts here
% ==========================================================================

\begin{document}

% ==========================================================================
% Summary
% ==========================================================================

\begin{tabularx}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\LARGE Alejandro Beltran} & \small{Email: alebelcor@gmail.com}\\
    & \small{GitHub: \href{https://github.com/alebelcor}{github.com/alebelcor}}\\
    & \small{LinkedIn: \href{https://linkedin.com/in/alebelcor}{linkedin.com/in/alebelcor}}\\\\
\end{tabularx}

\small I'm a Software Engineer from Mexico focused on Web Front End with 10+ years of experience with a specialty and passion for UI/UX, Web performance, and Web accessibility.

% ==========================================================================


% ==========================================================================
% Employment
% ==========================================================================

\section{Employment}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Senior Frontend Engineer}{\href{https://www.consumertrack.com/}{ConsumerTrack, Inc. \externalLink \footnote{Full-time}}}{Feb 2021 – Present}
    \resumeSubheading
      {Frontend Engineer}{\href{https://www.consumertrack.com/}{ConsumerTrack, Inc. \externalLink \footnote{via \href{https://www.encora.com/}{Encora}}}}{Apr 2020 – Feb 2021}
      \resumeItemListStart
        \resumeItem
          {Working remotely, focused on Frontend Engineering for \href{https://www.gofreecredit.com}{GOFreeCredit.com \externalLink} and \href{https://www.importantscore.com}{ImportantScore.com \externalLink} providing consumers easy, fast, and secure online access to their credit score and credit monitoring services via the national credit bureaus: Experian, and TransUnion}
        \resumeItem
          {Leading the migration and modernization of GOFreeCredit.com's Frontend Tech Stack with a system of reusable, composable, and themeable (via Design Tokens) component library.}
        \resumeItem
          {Led Web performance efforts to improve our performance score and Web Vitals, as part of our team mission, which has resulted in a 68\% (mobile) and 17\% (desktop) increase in performance score points for GOFreeCredit.com. And a 43\% (mobile) and 17\% (desktop) increase for ImportantScore.com.}
        \resumeItem
          {Led and implemented styling architecture and strategy for \href{https://www.gofinancialadvice.com}{GOFinancialAdvice.com \externalLink} resulting in $<$5 kB, code linting, auto formatting, testing, and their integrations to the developer flow (VS Code, hooks, etc.) and in CircleCI.}
        \resumeItem
          {Implemented several other performance optimizations: next-gen image formats, image optimizations, visible text during webfont load, reduced requests size, eliminated dead dependencies, added resource hints, asynchronous/lazy loading of images and render-blocking resources.}
        \resumeItem
          {Implemented A/B tests and experiments to determine the most successful variation to integrate and help increase revenue, gross profit, GPM, and various other C2C rates.}
        \resumeItem
          {Implemented automation of data management for CCPA compliance and to reduce the manual work of over 600 inquiries per month for "Delete My Data", "See My Data" and "Do Not Sell My Data" requests.}
      \resumeItemListEnd
      {\small{Tech: HTML, CSS, Sass, styled-components, styled-jsx, CSS Modules, Tailwind CSS, Bootstrap, JavaScript, React, Redux, Next.js, Jest, React Testing Library, ESLint, Prettier, Stylelint, Amazon S3, AWS Lambda, Git}}

    \resumeSubheading
      {Frontend Engineer}{\href{https://americantours.com/}{AmericanTours International, LLC \externalLink \footnote{via \href{https://nearsoft.com/}{Nearsoft}}}}{Nov 2019 – Mar 2020 \footnote{Project funding ended due to COVID-19}}
      \resumeItemListStart
        \resumeItem
          {Worked remotely, focused on Frontend Engineering and leading an Engineering team of two in charge of implementing a modern, fast, and aesthetic re-imagining of ATI's internal administration tool used by travel agents for payment and transaction review, and processing.}
        \resumeItem
          {Designed the shapes, payload/content, and headers of the HTTP API requests and responses.}
        \resumeItem
          {Implemented pure client-side user session management.}
        \resumeItem
          {Implemented auto-refresh mechanism of JWT tokens for authentication and authorization requests via renderless component for the duration of the user session.}
        \resumeItem
          {Implemented data tables with pagination, sorting, expandable rows with sub-component rendering.}
        \resumeItem
          {Implemented custom column filters for tables, e.g. text, date (with date picker widget), number range, and select.}
        \resumeItem
          {Implemented test suite or unit and integration tests with 90\% code coverage for actions/components/hooks/reducers/selectors/services/utils.}
        \resumeItem
          {Implemented maintainable and customizable CSS architecture using Sass, Bootstrap (with overrides), and BEM.}
        \resumeItem
          {Implemented mock back end API server using Express for faster and better DX.}
        \resumeItem
          {Integrated code linting and auto-formatting for JS/JSX files as part of test suite, and VS Code.}
      \resumeItemListEnd
      {\small{Tech: HTML, CSS, Sass, JavaScript, React, React Bootstrap, React Router, Reselect, Jest, React Testing Library, Create React App, ESLint, Prettier, SVN with git-svn}\vspace{28pt}}

    \resumeSubheading
      {Software Engineer (Front End)}{\href{https://www.switchfly.com/}{Switchfly, LLC \externalLink \footnote{via \href{https://nearsoft.com/}{Nearsoft}}}}{Feb 2014 – Aug 2019}
      \resumeItemListStart
        \resumeItem
          {Worked remotely, focused on Frontend Engineering and maintenance of a SaaS platform that powers travel, loyalty, social, payment, and mobile products for multiple clients.}
        \resumeItem
          {Implemented interstitial/loading page for better SEO and accessibility.}
        \resumeItem
          {Implemented custom responsive navigation with auto-collapsing items based on viewport.}
        \resumeItem
          {Increased performance by implementing preloading of the next page assets.}
        \resumeItem
          {Increased performance by reducing/consolidating–and compression–of Ajax HTTP requests/responses.}
        \resumeItem
          {Integrated \href{https://www.payback.net/de/en/home/}{PAYBACK® \externalLink} and \href{https://www.mastercard.us/}{Masterpass™ \externalLink} payment options into checkout process.}
        \resumeItem
          {Added automated end-to-end test cases for all new features in Selenium Java.}
        \resumeItem
          {Added base, and custom analytics for clients, for data-based product and UI/UX decision making.}
        \resumeItem
          {Refactored codebase to meet AA level of the WCAG 2.0 accessibility standard.}
        \resumeItem
          {Peer-reviewed other people's code as "Subject Matter Expect" of the shopping experience.}
      \resumeItemListEnd
      {\small{Tech: HTML, CSS, Sass, JavaScript, Ember.js, Java, Spring MVC, Selenium, Git, Mocha, Chai}}

    \resumeSubheading
      {Senior Frontend Engineer}{\href{https://evolvemediallc.com/}{Evolve Media, LLC \externalLink \footnote{via \href{https://intugo.co/}{Intugo}}}}{Jul 2013 – Feb 2014}
    \resumeSubheading
      {Frontend Engineer}{\href{https://evolvemediallc.com/}{Evolve Media, LLC \externalLink \footnotemark[6]}}{Jul 2012 – Jul 2013}
      \resumeItemListStart
        \resumeItem
          {Worked remotely, focused on Frontend Engineering for multiple heavily trafficked and highly ranked websites targeting, among other things: women, fashion, sports, gaming and entertainment.}
        \resumeItem
          {Examples: \href{https://www.thefashionspot.com/}{theFashionSpot \externalLink}, \href{https://www.momtastic.com/}{Momtastic \externalLink}, \href{https://www.superherohype.com/}{SuperHeroHype \externalLink}}
      \resumeItemListEnd
      {\small{Tech: HTML, CSS, Sass, JavaScript, jQuery, PHP, WordPress, SVN with git-svn}}

    \resumeSubheading
      {Application Development Engineer}{\href{https://www.optum.com/}{OptumInsight \externalLink \footnotemark[5]}}{Jan 2009 – Jun 2012}
      \resumeItemListStart
        \resumeItem
          {Worked remotely, as Application Development Engineer, extending and maintaining an EMR Lite system, related services, and applications.}
      \resumeItemListEnd
      {\small Tech: HTML, CSS, JavaScript, Java, Servlets, Lotus Notes/Domino, XML, XPath, XSLT, SVN}

  \resumeSubHeadingListEnd

% ==========================================================================


% ==========================================================================
% Education
% ==========================================================================

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bachelor of Computer Systems Engineering}{\href{http://ith.mx/}{Hermosillo Institute of Technology \externalLink}}{Dec 2008}
  \resumeSubHeadingListEnd

% ==========================================================================


% ==========================================================================
% Certifications
% ==========================================================================

\section{Certifications}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.freecodecamp.org/certification/alebelcor/responsive-web-design}{Responsive Web Design \externalLink}}{}{\href{https://www.freecodecamp.org/}{freeCodeCamp \externalLink}}
    \resumeSubheading
      {\href{https://www.freecodecamp.org/certification/alebelcor/javascript-algorithms-and-data-structures}{JavaScript Algorithms and Data Structures \externalLink}}{}{\href{https://www.freecodecamp.org/}{freeCodeCamp \externalLink}}
    \resumeSubheading
      {Scrum Foundation Professional Certificate}{}{\href{https://certiprof.com/pages/scrum-foundation-professional-certificate-sfpc-en-sp}{Scrum Foundation \externalLink}}
      {\tiny{\upshape{TLSZSQSVHG-MMSTYQSQ-RPFDLKRHJT}}}{}
  \resumeSubHeadingListEnd

% ==========================================================================


% ==========================================================================
% Skills
% ==========================================================================

\section{Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Software Engineering}{: Agile Software Development, Software Release Cycle, Unit Testing, Integration Testing, End-to-end Testing, Continuous Integration, Software Security, Static Code Analysis}
    }
    \item{
      \textbf{Front End (Web)}{: HTML, CSS, JavaScript, Web Performance, Web Accessibility, React, React Hooks, Redux, CSS-in-JS, Sass (SCSS), Bootstrap}
    }
    \item{
      \textbf{Tools}{: Node.js, npm, Yarn, ESLint, Prettier, Jest, React Testing Library, Git, Visual Studio Code}
    }
  \resumeSubHeadingListEnd

% ==========================================================================


% ==========================================================================
% Projects
% ==========================================================================

% \section{Projects}
%   \resumeSubHeadingListStart
%     \item\small{
%       \textbf{Project name}{: Project description. \vspace{-2pt}}
%     }
%   \resumeSubHeadingListEnd

% ==========================================================================

\end{document}
